---
title: "Behind the enum curtain"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(enumr)
```

## Enum structure

Under the surface, an enum is composed of two elements: a container environment, and a list. The list is what holds all the enum members. We can demonstrate this through a small example:

```{r}
my_enum <- enum(a, b, c)
my_list <- list(a = 1, b = 2, c = 3)
```

If the enum were identical to a list, we would expect `ls()` to return the same result for both objects

```{r}
ls(my_enum)
ls(my_list)
```

Why does `ls()` not return the enum names, like the list object? This is because `ls()` is returning the contents of the *container environment*, which is a list called enum. We can see the contents of the list like so:

```{r}
ls.str(my_enum)
```

## Why structure enums like this?

In order to define a static object (i.e. an object that cannot be re-defined), R has the `lockEnvironment()` method, which (to simplify) prevents changes to an environment and its contents. In {enumr}, we use `lockEnvironment()` to ensure that enum members cannot be changed after their definition, preventing the occurrence of 'magic values' ^[Values that have unexplained meanings, such as '0' and '1' referring to a categorical variable].

```{r,  error = TRUE}
a <- new.env()
a$enum <- list("some data")
lockEnvironment(a, bindings = TRUE)
a$enum <- "re-definition"
```

However, a downside for a list-type data structure is that environments have no concept of order. If we were to define a series of values, we couldn't be sure that the structure had the same order as how we intended. This means that if were to subset with an index (e.g. `[[1]]`), we might get a different value than what we were expecting.

```{r}
a <- new.env()
a$b <- 5
a$a <- "a string"
a$c <- 7

as.list(a)[[1]]
```

To circumvent this, we instead create a list *inside* the environment. This allows us to have the benefits of an ordered data structure, and still lock the values of the enum.
