---
title: "Typed Integration"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(c(typed, enummr), quietly = TRUE)
```


If you are using typed, you can make use of the `Enum` assertion for return and input assertion. Note that 'enum' is the class definition and 'Enum' is the assertion - this matches the {typed} paradigm of assertions.

Depending on how you define a variable, you can constrain a variable to either an enum class or enum member. To constrain to an enum class, simply use `Enum()`. To constrain to an enum member, use `Enum(x)`, with x being an enum.

For instance, let's say we want to ensure that the arguments supplied to a function correspond to an enum member value. Let's create an enum with a list of animals:

```{r, error = TRUE}
my_pets <- enum(
  pet1 = "dog",
  pet2 = "cat",
  pet3 = "goldfish"
)
```

Now, I want to make a function that only allows the my_pets enum as an argument:

```{r, error = TRUE}
# supply my_pets in the Enum assertion
is_this_my_pet <- ? function(arg = ? Enum(my_pets)) {
    print(arg)
}

# supply an incorrect argument
is_this_my_pet('snake')
```

See [{typed}](https://moodymudskipper.github.io/typed/) for more information on how to use these assertions.