---
title: "Non-Standard Evaluation"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include = FALSE}
library(enumr, quietly = TRUE)
```

You can use `.` (called "dot") to refer to the current enum. Due to this, when defining variables, you can use `.$` to refer to other elements in the enum. E.g.

```{r}
# Numeric enum
enum(
    a,
    b,
    c = .$a + 10,
    d = .$c * .$b
)

enum(
    a = "Hello",
    b = c(.$a, "world")
)

```

This means you can do some neat stuff with enum definition. For example:

```{r}
enum(
    base = "www.test.com/%s",
    download = sprintf(
        .$base,
        "download"
    ),
    upload = sprintf(
        .$base,
        "upload"
    )
)
```

### Limitations

It should be noted, however, there are limitations to defining members with `.$`. Firstly, enum member validation is performed *sequentially*. That is, each non-explicit member is initialised in order of their definition. We can see how this plays out "under the hood" by using the dot operator:

```{r}
enum(
    a = .,
    b = .,
    c = .
)
```

As above, the enum structure changes with each member's definition (remember that the dot operator refers to the current enum).

As a result, computed members cannot refer to later *non-explicit* members. For instance:

```{r, error = TRUE}
# Invalid definition!
enum(
    a,
    b = .$c + 1,
    c
)

# Valid due to explicit initialisation
enum(
    a,
    b = .$c + 1,
    c = 50
)

enum(
    a = .$c + 1,
    b = .$a + 1,
    c = 5
)
```

Moreover, due to sequential initialisation (and the pains of recursion), enum members do not support cyclical evaluation.

```{r, error = TRUE}
# Invalid
enum(
    a = .$b + 1,
    b = .$c + 1,
    c = .$a + 1
)
```
