---
title: "Overhead & Performance Optimisation"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include = FALSE}
library(enumr, quietly = TRUE)
library(dplyr)
library(ggplot2)
```

Enum definition is reasonably fast, so will likely not be a bottleneck for the large majority of users. However, if speed is of concern, there are some things to keep in mind:

- Symbols and calls require evaluation, which generally slow enum creation
- Inferred numerics are slower than explicit numerics
- Generic enums are *typically* faster than numeric enums

Here is a microbenchmark, comparing the various forms of enum. Note that a `create_symbols` function is defined for the generic_symbols parse. Realistically, generic and generic_symbols have comparable speeds.

```{r, echo=FALSE, message=FALSE}
# Create some symbols in the environment
# for benchmarking
create_symbols <- function() {
  mapply(
    function(x, y) assign(x, as.character(y), .GlobalEnv),
    c("a", "b", "c", "d", "e"),
    seq(5)
  )
}

res <- microbenchmark::microbenchmark(
    inferred <- enum(a, b, c, d, e),
    explicit_num_symbols <- enum(
        a = 1,
        b = .$a + 1,
        c = .$b + 1,
        d = .$c + 1,
        e = .$d + 1
        ),
    explicit_numeric <- enum(a = 1, b = 2, c = 3, d = 4, e = 5),
    {
        create_symbols()
        generic_symbols <- enum(a = a, b = b, c = c, d = d, e = e)
    },
    generic <- enum(a = "1", b = "2", c = "3", d = "4", e = "5"),
    times = 5000
)

res %>%
  autoplot() +
  scale_x_discrete(
    labels =
      c(
        "inferred\nenum(a, b, c, d, e)",
        "explicit_num_symbols\nenum(a = 1, b = .$a + 1...)",
        "explicit_numeric\nenum(a = 1, b = 2, c = 3, d = 4, e = 5)",
        "generic_symbols\nenum(a = a, b = b, c = c, d = d, e = e)",
        "generic\nenum(a = '1', b = '2', c = '3', d = '4', e = '5')"
      )
  )
```

To speed up performance further, you can also access the enum constructor methods directly: `new_generic_enum()` and `new_numeric_enum()`. You'll see these are reasonably faster than the `enum()` function (the speed increase will likely be in the microsecond range). This is because `enum()` has to check whether the enum is numeric or generic by evaluating each argument supplied to it.

```{r,  echo=FALSE, message=FALSE}
res2 <- microbenchmark::microbenchmark(
  num <- enum(x, y, z),
  num2 <- new_numeric_enum(list(x = 1, y = 2, z = 3)),
  gen <- enum(x = "1", y = "2", z = "3"),
  gen2 <- new_generic_enum(list(x = "1", y = "2", z = "3")),
  times = 5000
)

res2 %>%
  autoplot() +
  scale_x_discrete(
    labels = c(
      "num\nenum(x, y, z)",
      "gen\nenum(x = '1', y = '2', z = '3')",
      "num2\nnew_numeric_enum(list(x = 1, y = 2, z = 3))",
      "gen2\nnew_generic_enum(list(x = '1', y = '2', z = '3'))"
    )
  )
```

However, this forgoes some of the niceties of the `enum()` helper function, such as NSE or implicit definition.

```{r, error = TRUE}
# Can only use explicit definitions
new_numeric_enum(list(a, b, c))

# Can't use NSE
new_numeric_enum(list(a = 1, b = .$a + 1, c = 4))
```

Technically, you can use `substitute()` to still make use of the dot prefix, but this can be cumbersome after a while.

```{r}
new_numeric_enum(list(x = 5, y = substitute(.$x + 5)))
```